---
title: "Project Proposal"
subtitle: "2020 Vision"
author: "Mihir Patel, Tina Xia, Leah Okamura, Kyra Cooperman"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
sanfrancrime <- 
  read_csv("data/Police_Department_Incidents_-_Previous_Year__2016_.csv")
```

### Section 1

The subject matter we’re investigating is information about the crime in San Francisco. We're planning on analyzing the data and visualizing it to draw conclusions. Dataset: https://www.kaggle.com/roshansharma/sanfranciso-crime-dataset 

Research Question: What factors will allow the general population of San Francisco to be 
safest from local crime?

Motivation: In recent years, San Francisco hasn't been the safest place to live; the overall crime rate in San Francisco is 151% higher than the national average. According to SFChronicle, "homicides increased by 21.4% in San Francisco from March to June of this year," compared to 2019 (https://www.sfchronicle.com/bayarea/article/Which-crimes-are-up-down-in-SF-during-15408485.php). There is a 1 in 15 chance of becoming a victim of any crime. We wanted to use this dataset to obtain conclusions about specific factors that correlate to higher levels of crime, which will hopefully inform us of some key insights we can keep during future travels.

Hypotheses: A later time (e.g. nighttime hours) correlates to a higher level or rate of crime. Location is correlated to levels of crime. 

```{r dataglimpse}
glimpse(sanfrancrime)
```
