---
title: "Project Draft"
subtitle: "2020 Vision"
author: "Mihir Patel, Tina Xia, Leah Okamura, Kyra Cooperman"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
sanfrancrimeBIG <- 
  read_csv("data/Police_Department_Incidents_-_Previous_Year__2016_.csv")
```

### Introduction & Data

The subject matter we’re investigating is information about crime in San 
Francisco. In recent years, San Francisco hasn't been the safest place to live; 
the overall crime rate in San Francisco is 151% higher than the national 
average. According to SFChronicle, "homicides increased by 21.4% in San 
Francisco from March to June of this year," compared to 2019 (https://www.sfchronicle.com/bayarea/article/Which-crimes-are-up-down-in-SF-during-15408485.php). 
There is a 1 in 15 chance of becoming a victim of any crime. We wanted to use 
this dataset to obtain conclusions about specific factors that correlate to 
higher levels of crime, which will hopefully inform us of some key insights we 
can keep during future travels.

Research Question: What factors can the general population associate with local 
crime in order to be the safest while in San Francisco (or in other cities with similar characteristics)?

Hypotheses: A later time (e.g. nighttime hours) correlates to a higher level or 
rate of crime. Location is correlated to levels of crime. 

We are interested in these two hypotheses because we believe they can then lead 
to other interesting relationships between variables within this dataset. For 
example, if there is a strong correlation between night and rate of crime, then 
is there a correlation between which night of the week (ex. Sunday night) and 
rate of crime? With location, are there certain districts that have a specific 
crime that is common there? By delving further and examining these 
relationships, we will be able to understand if crime has any specific pattern 
in San Francisco. 

The observations in the dataset are of crime data in San Francisco from 2016. We
found our dataset at https://www.kaggle.com/roshansharma/sanfranciso-crime-dataset. 
Each observation in this datase is a crime whose various aspects have been 
recorded. There were originally 150,500 individual crimes/observations in this 
dataset. However, because of the nature of R Studio through OIT, we will be
taking a random and reproducible sample from the larger dataset. We created this
sample by using the function sample_n() on sanfrancrimeBIG to randomly select 
15,000 observations. We chose 15,000 because it is still large enough to get an 
accurate portrayal of the total data set, yet is much more manageable to process.


There are 13 variables in the dataset:
IncidntNum (double): gives the Incident Number of the crime
Category (character): gives category of crime
Description (character): gives description of crime
DayofWeek (character): gives day of week the crime occurred on
Date (character): gives date (day, month, and year) of crime
Time (double): gives time of crime (in military time)
PdDistrict (character): gives police district crime occurred in
Resolution (character): gives kind of punishment given to the criminal to 
                        resolve the case
Address (character): gives address where the crime happened
X (double): gives latitude of crime location
Y (double): gives longitude of crime location
Location (character): exact location using latitude and longitude
PdId (double): ID of police officer


The curator of the dataset got it from the final assignment for Coursera and 
IBM's Data Visualization Course. The information in this dataset is most likely
directly from the San Francisco Police Department for their reported crimes 
during 2016. This dataset was originally used to practice analyzing and 
visualizing data through geo spatial mapping by using folium maps for 
geographical understanding. 

### Methodology

The statistical methods we believe will be useful in answering our research 
question include the CLT, simulated null distributions, bootstrapping, etc. 
We're using these because certain variables are categorical, so they ETC ETC

Note: we plan on grouping violence based on violent vs nonviolent.

```{r dataglimpse}
sanfrancrime <- sanfrancrimeBIG %>%
  sample_n(15000)
  glimpse(sanfrancrime)
```

Variables we're considering:
Category
Day of Week
Date
Time
PdDistrict
Resolution


### Results
Showcase how you arrived at answers to your question using any techniques we have learned in this class (and some beyond, if you’re feeling adventurous). Provide the main results from your analysis. The goal is not to do an exhaustive data analysis, but rather let me know that you are proficient at asking meaningful questions and answering them with results of data analysis, that you are proficient in using R, and that you are proficient at interpreting and presenting the results. Focus on methods that help you begin to answer your research questions.

Research Question: What factors can the general population associate with local 
crime in order to be the safest while in San Francisco (or in other cities with similar characteristics)?



Relationship between category and time? Mihir

To determine the relationship between category and time, I have created 4 time 
intervals ( morning, day, evening, and night) and categorized the crimes based 
on the type of crime. I will then be performing a Chi-Squared test between these
categorical variables to determine if there is any relationship between them? (is that the right explanation).

```{r mihir creating time and filtering for important variables}
important <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr)) %>% 
  select(Category, DayOfWeek, Date, PdDistrict, Resolution, hour)

important <- important %>% 
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "night",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "day",
                                hour >= 18 & hour < 24 ~ "evening"))
glimpse(important)
```

```{r categorizing crime by type}
important <- important %>% 
  mutate(crimetype = case_when(
    
    Category == "BURGLARY" | Category == "LARCENY/THEFT" | 
    Category == "STOLEN PROPERTY" | Category == "RECOVERED VEHICLE" |
    Category == "VEHICLE THEFT" | Category == "ARSON" |
    Category == "VANDALISM"  ~ "property related",
    
    Category == "ROBBERY" | Category == "ASSAULT" | 
    Category == "KIDNAPPING" ~ "violence related",
    
    Category == "BRIBERY" | Category == "BAD CHECKS" | 
    Category == "EMBEZZLEMENT"| Category == "FORGERY/COUNTERFEITING" |
    Category == "FRAUD" | Category == "GAMBLING"| 
    Category == "EXTORTION" ~ "money related",
    
    Category == "DRIVING UNDER THE INFLUENCE" | Category == "DRUG/NARCOTIC" | 
    Category == "DRUNKENNESS"| Category == "LIQUOR LAWS" ~ "drug related",
    
    Category == "PORNOGRAPHY/OBSCENE MAT" | Category == "PROSTITUTION" | 
    Category == "SEX OFFENSES, FORCIBLE"| 
    Category == "SEX OFFENSES, NON FORCIBLE" ~ "sex related",

    Category == "LOITERING" | Category == "TREA" | 
    Category == "TRESPASS"| Category == "SUSPICIOUS OCC" |
    Category == "DISORDERLY CONDUCT" ~ "suss related",

    Category == "FAMILY OFFENSES" | Category == "MISSING PERSON" | 
    Category == "NON-CRIMINAL"| Category == "OTHER OFFENSES" |
    Category == "TRESPASS"| Category == "SECONDARY CODES" |
    Category == "SUICIDE"| Category == "SECONDARY CODES" |
    Category == "WARRANTS"| Category == "WEAPON LAWS" |
    Category == "RUNAWAY" ~ "misc."))

glimpse(important)
```


$H_0:$ NO relationship between the crime types created above and categories for
time of day created above.

$H_a:$ There IS a relationship between the crime types created above and 
categories for time of day created above.

$\alpha$ of 0.05

```{r chi-squared time}
crimecount <- important %>%
  count(crimetype)
crimecount
test <- important %>%
  group_by(crimetype) %>%
  count(timerange)
test

crimestuff <- c(rep(crimecount$crimetype[1], crimecount$n[1]),
               rep(crimecount$crimetype[2], crimecount$n[2]),
               rep(crimecount$crimetype[3], crimecount$n[3]),
               rep(crimecount$crimetype[4], crimecount$n[4]),
               rep(crimecount$crimetype[5], crimecount$n[5]),
               rep(crimecount$crimetype[6], crimecount$n[6]),
               rep(crimecount$crimetype[7], crimecount$n[7]))

timestuff <- c(
rep(test$timerange[1], test$n[1]), rep(test$timerange[2], test$n[2]), 
rep(test$timerange[3], test$n[3]), rep(test$timerange[4], test$n[4]),

rep(test$timerange[5], test$n[5]), rep(test$timerange[6], test$n[6]), 
rep(test$timerange[7], test$n[7]), rep(test$timerange[8], test$n[8]),

rep(test$timerange[9], test$n[9]), rep(test$timerange[10], test$n[10]), 
rep(test$timerange[11], test$n[11]), rep(test$timerange[12], test$n[12]),

rep(test$timerange[13], test$n[13]), rep(test$timerange[14], test$n[14]), 
rep(test$timerange[15], test$n[15]), rep(test$timerange[16], test$n[16]),

rep(test$timerange[17], test$n[17]), rep(test$timerange[18], test$n[18]), 
rep(test$timerange[19], test$n[19]), rep(test$timerange[20], test$n[20]),

rep(test$timerange[21], test$n[21]), rep(test$timerange[22], test$n[22]), 
rep(test$timerange[23], test$n[23]), rep(test$timerange[24], test$n[24]),

rep(test$timerange[25], test$n[25]), rep(test$timerange[26], test$n[26]), 
rep(test$timerange[27], test$n[27]), rep(test$timerange[28], test$n[28]))


table <- table(crimestuff, timestuff)

chisq.test(table)
```

The test statistic is 365.65, which has a chi squared distribution with 18
df under $H_0$. The p-value is < 2.2e-16 which is less than the $\alpha$ 
of 0.05. This means there is sufficient evidence to reject the null 
hypothesis. As a result, I conclude that there is sufficient evidence to 
suggest that at the 0.05 significance level that there is a relationship between
the crime types created above and categories for time of day created above.



Relationship between time and crime (ie do crimes generally occur at night)? Tina

Question: Are more crimes at night in San Francisco? We will construct an effective, well-labeled visualization of the crime count and time.

```{r crimesnightSF}
sanfrancrime <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr))

sanfrancrime <- sanfrancrime %>% 
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "night",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "day",
                                hour >= 18 & hour < 24 ~ "evening"))

sanfrancrime <- sanfrancrime %>% 
  group_by(Category) %>% 
  summarise(count = n())
sanfrancrime

ggplot(data = sanfrancrime, aes(x = timerange, y = count)) +
  geom_bar() + facet_grid(~Category) + labs(x = "time", y = "Count of Crimes",
title = "SSS")

```


Which PD has the highest proportion of violent crime? Kyra

Day of the week and category? Leah
ETC!


```{r PD vs Violent Crime}
sanfrancrime%>%
  group_by(Category)%>%
  count()
sanfrancrime<- sanfrancrime%>%
  mutate(violent_crime = case_when(
    Category == "ASSAULT" | Category == "SEX OFFENSES FORCIBLE" | 
      Category == "ROBBERY" | Category == "KIDNAPPING" ~ "YES",
    Category != "ASSAULT" | Category != "SEX OFFENSES, FORCIBLE" |
      Category != "ROBBERY" | Category !="KIDNAPPING" ~ "NO"))
sanfrancrime%>%
  group_by(PdDistrict)%>%
  mutate(yes_violent = violent_crime == "YES")%>%
  count(yes_violent)%>%
  mutate(perc = (n/sum(n) *100))%>%
  filter(yes_violent == TRUE)%>%
  arrange(desc(perc))


```



### Discussion
This section is a conclusion and discussion. This will require a summary of what you have learned about your research question along with statistical arguments supporting your conclusions. Also, critique your own methods and provide suggestions for improving your analysis. Issues pertaining to the reliability and validity of your data and appropriateness of the statistical analysis should also be discussed here. A paragraph on what you would do differently if you were able to start over with the project or what you would do next if you were going to continue work on the project should also be included.

