---
title: "Project Proposal"
subtitle: "2020 Vision"
author: "Mihir Patel, Tina Xia, Leah Okamura, Kyra Cooperman"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
sanfrancrime <- 
  read_csv("data/Police_Department_Incidents_-_Previous_Year__2016_.csv")
```

Sanfrancisco-Crime-Dataset
This Problem Data set of San Francisco Contains information about the crime in San Francisco, We are going to analyze the data, Visualize the data using folium maps for geographical understanding. In other words It is called Geo spatial Mapping. This Problem is the final assignment for Coursera and IBM's Data Visualization Course.

some facts
The overall crime rate in San Francisco is 151% higher than the national average.

For every 100,000 people, there are 18.86 daily crimes that occur in San Francisco.

San Francisco is safer than 5% of the cities in the United States.

In San Francisco you have a 1 in 15 chance of becoming a victim of any crime.

The number of total year over year crimes in San Francisco has not changed.



In recent years, San Francs


RQ: What factors will allow the general population of San Francisco to be 
safest from local crime?

Hypotheses: 

```{r dataglimpse}
glimpse(sanfrancrime)
```
