---
title: "Project Draft"
subtitle: "2020 Vision"
author: "Mihir Patel, Tina Xia, Leah Okamura, Kyra Cooperman"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
sanfrancrimeBIG <- 
  read_csv("data/Police_Department_Incidents_-_Previous_Year__2016_.csv")
```

### Introduction

The subject matter we’re investigating is information about crime in San 
Francisco. In recent years, San Francisco hasn't been the safest place to live; 
the overall crime rate in San Francisco is 151% higher than the national 
average. According to SFChronicle, "homicides increased by 21.4% in San 
Francisco from March to June of this year," compared to 2019 (https://www.sfchronicle.com/bayarea/article/Which-crimes-are-up-down-in-SF-during-15408485.php). 
There is a 1 in 15 chance of becoming a victim of any crime. We wanted to use 
this dataset to obtain conclusions about specific factors that correlate to 
higher levels of crime, which will hopefully inform us of some key insights we 
can keep during future travels.

https://www.sfchronicle.com/bayarea/philmatier/article/SF-ranks-high-in-property-crime-while-it-ranks-14439369.php

Research Question: What factors can the general population associate with local 
crime in order to be the safest while in San Francisco (or in other cities with similar characteristics)?

Hypotheses: A later time (e.g. nighttime hours) correlates to a higher level or 
rate of crime. Location is correlated to levels of crime. 

We are interested in these two hypotheses because we believe they can then lead 
to other interesting relationships between variables within this dataset. For 
example, if there is a strong correlation between night and rate of crime, then 
is there a correlation between which night of the week (ex. Sunday night) and 
rate of crime? With location, are there certain districts that have a specific 
crime that is common there? By delving further and examining these 
relationships, we will be able to understand if crime has any specific pattern 
in San Francisco. 


### Data 

```{r dataglimpse}
set.seed(1)
sanfrancrime <- sanfrancrimeBIG %>%
  sample_n(15000)
  glimpse(sanfrancrime)
```

The observations in the dataset are of crime data in San Francisco from 2016. We
found our dataset at https://www.kaggle.com/roshansharma/sanfranciso-crime-dataset. 
Each observation in this datase is a crime whose various aspects have been 
recorded. There were originally 150,500 individual crimes/observations in this 
dataset. However, because of the nature of R Studio through OIT, we will be
taking a random and reproducible sample from the larger dataset. We created this
sample by using the function sample_n() on sanfrancrimeBIG to randomly select 
15,000 observations. We chose 15,000 because it is still large enough to get an 
accurate portrayal of the total data set, yet is much more manageable to process.

There are 13 variables in the dataset:
IncidntNum (double): gives the Incident Number of the crime
Category (character): gives category of crime
Description (character): gives description of crime
DayofWeek (character): gives day of week the crime occurred on
Date (character): gives date (day, month, and year) of crime
Time (double): gives time of crime (in military time)
PdDistrict (character): gives police district crime occurred in
Resolution (character): gives kind of punishment given to the criminal to 
                        resolve the case
Address (character): gives address where the crime happened
X (double): gives latitude of crime location
Y (double): gives longitude of crime location
Location (character): exact location using latitude and longitude
PdId (double): ID of police officer

The curator of the dataset got it from the final assignment for Coursera and 
IBM's Data Visualization Course. The information in this dataset is most likely
directly from the San Francisco Police Department for their reported crimes 
during 2016. This dataset was originally used to practice analyzing and 
visualizing data through geo spatial mapping by using folium maps for 
geographical understanding. 


### Methodology

The statistical methods we believe will be useful in answering our research 
question include the CLT, simulated null distributions, bootstrapping, etc. 
We're using these because certain variables are categorical, so they ETC ETC

Note: we plan on grouping violence based on violent vs nonviolent.

Variables we're considering:
Category
Day of Week
Date
Time
PdDistrict
Resolution


### Results
Showcase how you arrived at answers to your question using any techniques we have learned in this class (and some beyond, if you’re feeling adventurous). Provide the main results from your analysis. The goal is not to do an exhaustive data analysis, but rather let me know that you are proficient at asking meaningful questions and answering them with results of data analysis, that you are proficient in using R, and that you are proficient at interpreting and presenting the results. Focus on methods that help you begin to answer your research questions.


### Relationship between category and time? Mihir

To determine the relationship between category and time, I have created 4 time 
intervals ( morning, day, evening, and night) and categorized the crimes based 
on the type of crime. I will then be performing a Chi-Squared test between these
categorical variables to determine if there is any relationship between them? (is that the right explanation).

```{r mihir creating time and filtering for important variables}
important <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr)) %>% 
  select(Category, DayOfWeek, Date, PdDistrict, Resolution, hour)

important <- important %>% 
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "night",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "day",
                                hour >= 18 & hour < 24 ~ "evening"))
glimpse(important)
```

```{r categorizing crime by type}
important <- important %>% 
  mutate(crimetype = case_when(
    
    Category == "BURGLARY" | Category == "LARCENY/THEFT" | 
    Category == "STOLEN PROPERTY" | Category == "RECOVERED VEHICLE" |
    Category == "VEHICLE THEFT" | Category == "ARSON" |
    Category == "VANDALISM"  ~ "Property",
    
    Category == "ROBBERY" | Category == "ASSAULT" | 
    Category == "KIDNAPPING" | 
      Category == "SEX OFFENSES, FORCIBLE" ~ "Violent",
    
    Category == "BRIBERY" | Category == "BAD CHECKS" | 
    Category == "EMBEZZLEMENT"| Category == "FORGERY/COUNTERFEITING" |
    Category == "FRAUD" | Category == "GAMBLING"| 
    Category == "EXTORTION" ~ "White Collar",
    
    Category == "DRIVING UNDER THE INFLUENCE" | Category == "DRUG/NARCOTIC" | 
    Category == "DRUNKENNESS"| Category == "LIQUOR LAWS" ~ "Drug/Alcohol",
    
    Category == "PORNOGRAPHY/OBSCENE MAT" | Category == "PROSTITUTION" |
    Category == "SEX OFFENSES, NON FORCIBLE" ~ "Sex",

    Category == "LOITERING" | Category == "TREA" | 
    Category == "TRESPASS"| Category == "SUSPICIOUS OCC" |
    Category == "DISORDERLY CONDUCT" ~ "Suspicious",
    
    Category == "WARRANTS"|Category == "WEAPON LAWS" |
    Category == "SECONDARY CODES" ~ "Legal Violation",

    Category == "MISSING PERSON" |Category == "NON-CRIMINAL"|
    Category == "OTHER OFFENSES" |Category == "SUICIDE"| 
    Category == "FAMILY OFFENSES" | Category == "RUNAWAY" ~ "Miscellaneous"))

glimpse(important)
```


$H_0:$ NO relationship between the crime types created above and categories for
time of day created above.

$H_a:$ There IS a relationship between the crime types created above and 
categories for time of day created above.
 
$\alpha$ of 0.05

```{r chi-squared time}

#Table needs to be fixed
crimecount <- important %>%
  count(crimetype)
crimecount
test <- important %>%
  group_by(crimetype) %>%
  count(timerange)
test

crimestuff <- c(rep(crimecount$crimetype[1], crimecount$n[1]),
               rep(crimecount$crimetype[2], crimecount$n[2]),
               rep(crimecount$crimetype[3], crimecount$n[3]),
               rep(crimecount$crimetype[4], crimecount$n[4]),
               rep(crimecount$crimetype[5], crimecount$n[5]),
               rep(crimecount$crimetype[6], crimecount$n[6]),
               rep(crimecount$crimetype[7], crimecount$n[7]))

timestuff <- c(
rep(test$timerange[1], test$n[1]), rep(test$timerange[2], test$n[2]), 
rep(test$timerange[3], test$n[3]), rep(test$timerange[4], test$n[4]),

rep(test$timerange[5], test$n[5]), rep(test$timerange[6], test$n[6]), 
rep(test$timerange[7], test$n[7]), rep(test$timerange[8], test$n[8]),

rep(test$timerange[9], test$n[9]), rep(test$timerange[10], test$n[10]), 
rep(test$timerange[11], test$n[11]), rep(test$timerange[12], test$n[12]),

rep(test$timerange[13], test$n[13]), rep(test$timerange[14], test$n[14]), 
rep(test$timerange[15], test$n[15]), rep(test$timerange[16], test$n[16]),

rep(test$timerange[17], test$n[17]), rep(test$timerange[18], test$n[18]), 
rep(test$timerange[19], test$n[19]), rep(test$timerange[20], test$n[20]),

rep(test$timerange[21], test$n[21]), rep(test$timerange[22], test$n[22]), 
rep(test$timerange[23], test$n[23]), rep(test$timerange[24], test$n[24]),

rep(test$timerange[25], test$n[25]), rep(test$timerange[26], test$n[26]), 
rep(test$timerange[27], test$n[27]), rep(test$timerange[28], test$n[28]))


table <- table(crimestuff, timestuff)

chisq.test(table)
```

The test statistic is 359.84, which has a chi squared distribution with 18
df under $H_0$. The p-value is < 2.2e-16 which is less than the $\alpha$ 
of 0.05. This means there is sufficient evidence to reject the null 
hypothesis. As a result, I conclude that there is sufficient evidence to 
suggest that at the 0.05 significance level that there is a relationship between
the crime types created above and categories for time of day created above.



### Relationship between time and crime? Tina

Question: Do more crimes generally occur at night in San Francisco? We will construct an effective, well-labeled visualization of the crime count and time.

```{r crimesnightSF}
sanfrancrime <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr))

sanfrancrime <- sanfrancrime %>%
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "dawn",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "afternoon",
                                hour >= 18 & hour < 24 ~ "night"))


ggplot(sanfrancrime, mapping = aes(y = timerange)) +
  geom_bar() + facet_wrap(~ Category) + labs(
    x = "Count",
    y = "Time of Day",
    title = "Relationship Between Category of Crime With Time of Day and Crime Count", subtitle = "Faceted by Category of Crime") + theme(axis.text = element_text(size = 7))

# sanfrancrime <- sanfrancrime %>% 
#   group_by(Category) %>% 
#   summarise(count = n())
# sanfrancrime

```

After constructing our visualization of crime count and time, a few things are clear: first, we can see that certain categories of crime are far more prominent than others. For example, larceny/theft is more common, along with non-criminal crimes, assault, and other crimes. Most crimes seem to happen during the afternoon and night, with the least happening in the hours from 0 to 6 (or in the early morning). Out of all the categories of crime listed, larceny/theft is mostly conducted during the evening, or between hours 18 & 24, ie between 6pm and 12am. This makes sense, as this is usually when night begins to set in, and it's a bit darker out, thus lending to increased obscurity and decreased acuity and vision-related impairments. Overall, this visualization was quite interesting to dissect, as there does seem to be a correlation between crimes and their time of occurrence, as more crimes occur during afternoons and evenings.

```{r map}
# library(sf)
# data1 <- st_read("data/Police_Department_Incidents_-_Previous_Year__2016_.csv", quiet = TRUE)
# data1

# ggplot(data1) +
#   geom_sf(aes(fill = voted)) +
#   labs(title = "Higher population counties have more votes cast",
#        fill = "Total number of votes cast") + 
#   theme_bw()
# 
# ggplot(data1) +
#   geom_sf(color = "green", size = 1.5, fill = "orange", alpha = 0.50) +
#   labs(title = "SF data with theme and aesthetics") +
#   theme_bw()
```
Office hrs



### Which PD has the highest proportion of violent crime? Kyra

```{r PD vs Violent Crime}
pd_violent <- sanfrancrime%>%
  group_by(Category)%>%
  count()
pd_violent<- sanfrancrime%>%
  mutate(violent_crime = case_when(
    Category == "ASSAULT" | Category == "SEX OFFENSES FORCIBLE" | 
      Category == "ROBBERY" | Category == "KIDNAPPING" ~ "YES",
    Category != "ASSAULT" | Category != "SEX OFFENSES, FORCIBLE" |
      Category != "ROBBERY" | Category !="KIDNAPPING" ~ "NO"))
important <- important%>%
  filter(PdDistrict!="NA")%>%
  group_by(PdDistrict)%>%
  mutate(yes_violent = crimetype == "violence related")%>%
  arrange(desc(yes_violent))


important%>%
  group_by(PdDistrict)%>%
  count(yes_violent)%>%
  mutate(perc = (n/sum(n)*100))%>%
  arrange(desc(perc))%>%
  filter(yes_violent=="TRUE")
  
ggplot(important, aes(x = PdDistrict, fill = yes_violent))+
  geom_bar(position = "fill") + coord_flip()+
  labs(title = 
         "Ingleside, Mission, and Tenderloin Have Highest Violent Crime Rates ",
       y = "Percentage of Violent Crimes", x = "Police District")


```


Ingleside, Mission, and Tenderloin have the highest rates of violent crime.
However, Mission, Southern, and Bayview have the highest number of violent crimes.
Park and Richmond both have the lowest rates and total numbers of violent crimes.
For all police districts, the percentage of violent crimes is lower than 16%.


### How does time range affect whether crimes are violent? Kyra

```{r}
library(broom)
mod<- lm(yes_violent~timerange, 
         data = important)
tidy(mod)


```

logit(p) = 0.10383 + 0.01188(evening) + 0.00227(morning) + 0.06939(night)


### Day of the week and category? Leah

```{r day of week and number of crimes}
#library(forcats)
#sanfrancrime <- sanfrancrime%>%
  #mutate(DayOfWeek = factor(DayOfWeek, labels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", #"Sunday"), levels = c(0,1,2,3,4,5,6)))
day <- sanfrancrime%>%
  group_by(DayOfWeek)%>%
  mutate(cpday = n())%>%
  select(DayOfWeek, cpday)
day
ggplot(data = day, mapping = aes(x = DayOfWeek)) +
    geom_bar()  + labs(x = "Day", y = "Count",
      title = "Number of Crimes Per Day Suggest Equal Spread of Crime") 
#need to change order of days of the week
```

One relationship we were interested in was if certain days had a higher rates of crime. We visualized this relationship by creating a bar graph that compares the day of the week and number of crimes each day during this time period. By looking at the visual, we are able to see that each has a relatively similar crime count compared to the other. In addition to this, there is no significant pattern that sticks out as well. 

```{r day and crimetype}
crimetypeday <-important%>%
  group_by(crimetype)%>%
  mutate(ctcount = n())
crimetypeday


ggplot(data = crimetypeday, mapping = aes(y = crimetype)) +
  geom_bar() + facet_wrap(~ DayOfWeek) +
  labs(
    x = "Count",
    y = "Type of Crime",
    title = "Type of Crime by Day Shows A Large Proportion of Crimes as 
    Property Related or Miscellaneous")

#need to fix crimetype names 
# make miscellaneous crimes more specific?
```

The faceted bar graph shows the frequency of each crime rate on a given day of the week. When looking at the visualization, it is easy to see the large difference between types of crime that exist. On each day, the number of property related crimes and miscellaneous crimes are significantly greater than the 5 other crime types. When looking at the frequency of crime types from day to day, every day has a similar pattern of frequency. This further supports the observation from the previous visualization where crime and day of the week do not necessarily have a relationship.



### Discussion
This section is a conclusion and discussion. This will require a summary of what you have learned about your research question along with statistical arguments supporting your conclusions. Also, critique your own methods and provide suggestions for improving your analysis. Issues pertaining to the reliability and validity of your data and appropriateness of the statistical analysis should also be discussed here. A paragraph on what you would do differently if you were able to start over with the project or what you would do next if you were going to continue work on the project should also be included.




