---
title: "Staying Safe: Analyzing Crime in San Francisco"
subtitle: "2020 Vision"
author: "Mihir Patel, Tina Xia, Leah Okamura, Kyra Cooperman"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
sanfrancrimeBIG <- 
  read_csv("data/Police_Department_Incidents_-_Previous_Year__2016_.csv")

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
```

### INTRODUCTION AND DATA


San Francisco is a city known for its strong economy and booming tech industry. 
In addition to Silicon Valley and San Jose, the Bay Area is home to many
powerful companies such as Google, Tesla, Apple, and Cisco. Because of these 
many benefits, San Francisco is a popular destination for college graduates. In 
May 2020, San Francisco was ranked second as the best metro area for recent 
graduates. This especially took into consideration the "high wages, work from 
home ability, and a (mainly) pandemic-resilient economy" that many recent 
graduates worry about during this time [1]. 

However, with an overall crime rate in San Francisco that is 151% higher than 
the national average, is it also important to note that in recent years, San 
Francisco has not been the safest place to live. The SFChronicle reported that 
compared to 2019, "homicides increased by 21.4% in San Francisco from March to 
June of this year,"[2]. There is a 1 in 15 chance of becoming a victim of any 
type of crime. A quick search about travel in San Francisco includes many 
articles listing the "Places to Avoid After Dark" or "Most Dangerous 
Neighborhoods in SF."With the a high possibility of any of us moving to San 
Francisco after our time at Duke,and the recent popularity with college 
graduates, we wanted to analyze this dataset to obtain conclusions about 
specific factors that correlate to higher levels of crime, which will could 
then inform us of some key insights we can keep during future travels or moves. 

Through our research, we plan to investigate what factors the general population
can associate with local crime in order to be the safest while in San Francisco.
Our main hypotheses are 1) a later time (e.g. nighttime hours) correlates to a 
higher level or rate of crime and 2) Location is correlated to levels of crime. 
We are interested in these two hypotheses because we believe they can then lead 
to other interesting relationships between variables within this dataset. For 
example, if there is a strong correlation between night and rate of crime, then 
is there a correlation between which night of the week (ex. Sunday night) and 
rate of crime? With location, are there certain districts that have a specific 
crime that is common there? By delving further and examining these 
relationships, we will be able to understand if crime has any specific pattern 
in San Francisco. 

```{r dataglimpse}
set.seed(1)
sanfrancrime <- sanfrancrimeBIG %>%
  sample_n(15000)
  glimpse(sanfrancrime)
```

The observations in the dataset are of crime data in San Francisco from 2016. We
found our dataset at https://www.kaggle.com/roshansharma/sanfranciso-crime-dataset. 
Each observation in this dataset is a crime whose various aspects have been 
recorded. There were originally 150,500 individual crimes/observations in this 
dataset. However, because of the nature of R Studio through OIT, we will be
taking a random and reproducible sample from the larger dataset. We created this
sample by using the function sample_n() on sanfrancrimeBIG to randomly select 
15,000 observations. We chose 15,000 because it is still large enough to get an 
accurate portrayal of the total data set, yet is much more manageable to process.

There are 13 variables in the dataset:
IncidntNum (double): gives the Incident Number of the crime
Category (character): gives category of crime
Description (character): gives description of crime
DayofWeek (character): gives day of week the crime occurred on
Date (character): gives date (day, month, and year) of crime
Time (double): gives time of crime (in military time)
PdDistrict (character): gives police district crime occurred in
Resolution (character): gives kind of punishment given to the criminal to 
                        resolve the case
Address (character): gives address where the crime happened
X (double): gives latitude of crime location
Y (double): gives longitude of crime location
Location (character): exact location using latitude and longitude
PdId (double): ID of police officer

The curator of the dataset got it from the final assignment for Coursera and 
IBM's Data Visualization Course. The information in this dataset is most likely
directly from the San Francisco Police Department for their reported crimes 
during 2016. This dataset was originally used to practice analyzing and 
visualizing data through geo spatial mapping by using folium maps for 
geographical understanding. 


### METHODOLOGY

### Variables

We will analyze the validity of our hypotheses using various statistical methods, including a Chi-square test, bootstrapping, and a logistic regression model, among others. Note: we plan on grouping violence based on violent vs nonviolent. The main variables we will be using in our analysis are Category, DayOfWeek, Date, Time, PdDistrict, and Resolution. We also created new variables to assist us in our data. This includes the variable timerange, that organizes the hour of the day into four times of day "night", "morning", "day", and "evening."
```{r mihir creating time and filtering for important variables}
important <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr)) %>% 
  select(Category, DayOfWeek, Date, PdDistrict, Resolution, hour)

important <- important %>% 
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "dawn",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "afternoon",
                                hour >= 18 & hour < 24 ~ "night"))
```
We also decided to categorize the all of the different types of crime that were reported. We organized the 39 types of crimes into varable crimetype, which consists of "Property", "Violent", "White Collar", "Drug/Alcohol", "Sex", "Suspicious", "Legal Violation", and "Miscellaneous".
```{r categorizing crime by type}
important <- important %>% 
  mutate(crimetype = case_when(
    
    Category == "BURGLARY" | Category == "LARCENY/THEFT" | 
    Category == "STOLEN PROPERTY" | Category == "RECOVERED VEHICLE" |
    Category == "VEHICLE THEFT" | Category == "ARSON" |
    Category == "VANDALISM"  ~ "Property",
    
    Category == "ROBBERY" | Category == "ASSAULT" | 
    Category == "KIDNAPPING" | 
      Category == "SEX OFFENSES, FORCIBLE" ~ "Violent",
    
    Category == "BRIBERY" | Category == "BAD CHECKS" | 
    Category == "EMBEZZLEMENT"| Category == "FORGERY/COUNTERFEITING" |
    Category == "FRAUD" | Category == "GAMBLING"| 
    Category == "EXTORTION" ~ "White Collar",
    
    Category == "DRIVING UNDER THE INFLUENCE" | Category == "DRUG/NARCOTIC" | 
    Category == "DRUNKENNESS"| Category == "LIQUOR LAWS" ~ "Drug/Alcohol",
    
    Category == "PORNOGRAPHY/OBSCENE MAT" | Category == "PROSTITUTION" |
    Category == "SEX OFFENSES, NON FORCIBLE" ~ "Sex",

    Category == "LOITERING" | Category == "TREA" | 
    Category == "TRESPASS"| Category == "SUSPICIOUS OCC" |
    Category == "DISORDERLY CONDUCT" ~ "Suspicious",
    
    Category == "WARRANTS"|Category == "WEAPON LAWS" |
    Category == "SECONDARY CODES" ~ "Legal Violation",

    Category == "MISSING PERSON" |Category == "NON-CRIMINAL"|
    Category == "OTHER OFFENSES" |Category == "SUICIDE"| 
    Category == "FAMILY OFFENSES" | Category == "RUNAWAY" ~ "Miscellaneous"))

glimpse(important)
```

### Visualizations

### 1- Relationship between crime type and time? Mihir

```{r random visualizations}
ggplot(data = important, mapping = aes(x = timerange)) +
  geom_bar(aes(fill = crimetype), position = "dodge") +
  labs(x = "Time of the Day", y = "Count of Crime Type", 
       title = "The most property crime happens in the Evening",
       subtitle = "The most violent crime happens in the Evening",
       fill= "Crime Type")

```


###2 - Relationship between time and crime? Tina

Question: Do more crimes generally occur at night in San Francisco? We will construct an effective, well-labeled visualization of the crime count and time.

```{r crimesnightSF}
sanfrancrime <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr))

sanfrancrime <- sanfrancrime %>%
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "dawn",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "afternoon",
                                hour >= 18 & hour < 24 ~ "night"))


ggplot(sanfrancrime, mapping = aes(y = timerange)) +
  geom_bar() + facet_wrap(~ Category) + labs(
    x = "Count",
    y = "Time of Day",
    title = "More Arceny/Theft, Assault and Non-Criminal Activity: the 
    Relationship Between Category of Crime With Time of Day and Crime Count", 
    subtitle = "Faceted by Category of Crime") + 
  theme(axis.text = element_text(size = 7))

# sanfrancrime <- sanfrancrime %>% 
#   group_by(Category) %>% 
#   summarise(count = n())
# sanfrancrime

```
After constructing our visualization of crime count and time, a few things are clear: first, we can see that certain categories of crime are far more prominent than others. For example, larceny/theft is more common, along with non-criminal crimes, assault, and other crimes. Most crimes seem to happen during the afternoon and night, with the least happening in the hours from 0 to 6 (or in the early morning). 

Out of all the categories of crime listed, larceny/theft is mostly conducted during the evening, or between hours 18 & 24, ie between 6pm and 12am. This makes sense, as this is usually when night begins to set in, and it's a bit darker out, thus lending to increased obscurity and decreased acuity and vision-related impairments. Overall, this visualization was quite interesting to dissect, as there does seem to be a correlation between crimes and their time of occurrence, as more crimes occur during afternoons and evenings.


```{r map-needs-geometry}
library(sf)
sfran <- st_read("data/Current Police Districts-2", quiet = TRUE)
sfran

ggplot(sfran) +
    geom_sf(color = "blue", size = 1.5, fill = "orange", alpha = 0.50) +
    labs(title = "Current Police Districts in San Francisco Singled Out on a Map") +
    theme_bw()

plot(sfran)
plot(sfran["shape_area"], key.pos = 4, main = "Areas of SF Districts Colored by Size")

```

links to use for map:
https://www.benjaminsorensen.me/project/sf_police/ 
https://data.sfgov.org/Public-Safety/Current-Police-Districts/wkhw-cjsf 
https://r-spatial.github.io/sf/articles/sf5.html#geometry-with-attributes-sf-1 

The purpose of this faceted barplot is to show which police districts have the
highest rate of crime, as well as the highest proportion of violent crimes.

### 3- Which PD has the highest proportion of violent crime? Kyra

```{r PD vs Violent Crime}
 # pd_violent <- sanfrancrime%>%
 #   group_by(Category)%>%
 #   count()

 important3 <- important

 important3 <- important%>%
   filter(PdDistrict!="NA")%>%
   group_by(PdDistrict)%>%
   mutate(yes_violent = crimetype == "Violent")%>%
   arrange(desc(yes_violent))


 important3%>%
   group_by(PdDistrict)%>%
   count(yes_violent)%>%
   mutate(perc = (n/sum(n)*100))%>%
   arrange(desc(perc))%>%
   filter(yes_violent=="TRUE")%>%
   select(PdDistrict, n, perc)
 

ggplot(important3, aes(x = PdDistrict, fill = yes_violent))+
  geom_bar(position = "fill") + coord_flip()+
  labs(title =
         "Ingleside, Mission, and Tenderloin Have Highest Violent Crime Rates ",
       y = "Proportion of Violent Crimes", x = "Police District")


```


By looking at the table and bar plot, it is clear that Ingleside, Mission, and 
Tenderloin have the highest rates of violent crime.
However, Mission, Southern, and Bayview have the highest number of violent crimes.
Park and Richmond both have the lowest rates and total numbers of violent crimes.
For all police districts, the percentage of violent crimes is lower than 18%. 


### 5- Day of the week and category? Leah

```{r day of week and number of crimes}
library(forcats)
sanfrancrime$DayOfWeek <- factor(sanfrancrime$DayOfWeek, levels= c("Sunday", "Monday", 
    "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
day <- sanfrancrime%>%
  group_by(DayOfWeek)%>%
  mutate(cpday = n())%>%
  select(DayOfWeek, cpday)
day
ggplot(data = day, mapping = aes(x = DayOfWeek)) +
    geom_bar()  + labs(x = "Day", y = "Count",
      title = "Number of Crimes Per Day Suggest Equal Spread of Crime") 
```

One relationship we were interested in was if certain days had a higher rates of crime. We visualized this relationship by creating a bar graph that compares the day of the week and number of crimes each day during this time period. By looking at the visual, we are able to see that each has a relatively similar crime count compared to the other. In addition to this, there is no significant pattern that sticks out as well. 

```{r day and crimetype}
important$DayOfWeek <- factor(important$DayOfWeek, levels= c("Sunday", "Monday", 
    "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
crimetypeday <-important%>%
  group_by(crimetype)%>%
  mutate(ctcount = n())
crimetypeday

ggplot(data = important, mapping = aes(x = DayOfWeek)) +
  geom_bar(aes(fill = crimetype), position = "dodge") +
  labs(x = "Day of the Week", y = "Count of Crime Type", 
       title = "The most property crime happens on Friday",
       subtitle = "The most violent crime happens on Saturday",
       fill= "Crime Type")
```

The faceted bar graph shows the frequency of each crime rate on a given day of the week. When looking at the visualization, it is easy to see the large difference between types of crime that exist. On each day, the number of property related crimes and miscellaneous crimes are significantly greater than the 5 other crime types. When looking at the frequency of crime types from day to day, every day has a similar pattern of frequency. This further supports the observation from the previous visualization where crime and day of the week do not necessarily have a relationship.


#Chi-Square Test

#Mihir
We will be performing a Chi-Squared test between these
crime types and categorical time of day to determine if there is the relationship between them is 
statistically significant.

$H_0:$ NO relationship between the crime types created above and categories for
time of day created above.

$H_a:$ There IS a relationship between the crime types created above and 
categories for time of day created above.
 
$\alpha$ of 0.05

```{r chi-squared time}

crimecount <- important %>%
  count(crimetype)

test <- important %>%
  group_by(crimetype) %>%
  count(timerange)

CrimeCategory <- c(rep(crimecount$crimetype[1], crimecount$n[1]),
               rep(crimecount$crimetype[2], crimecount$n[2]),
               rep(crimecount$crimetype[3], crimecount$n[3]),
               rep(crimecount$crimetype[4], crimecount$n[4]),
               rep(crimecount$crimetype[5], crimecount$n[5]),
               rep(crimecount$crimetype[6], crimecount$n[6]),
               rep(crimecount$crimetype[7], crimecount$n[7]),
               rep(crimecount$crimetype[8], crimecount$n[8]))

TimeOfDay <- c(
rep(test$timerange[1], test$n[1]), rep(test$timerange[2], test$n[2]), 
rep(test$timerange[3], test$n[3]), rep(test$timerange[4], test$n[4]),

rep(test$timerange[5], test$n[5]), rep(test$timerange[6], test$n[6]), 
rep(test$timerange[7], test$n[7]), rep(test$timerange[8], test$n[8]),

rep(test$timerange[9], test$n[9]), rep(test$timerange[10], test$n[10]), 
rep(test$timerange[11], test$n[11]), rep(test$timerange[12], test$n[12]),

rep(test$timerange[13], test$n[13]), rep(test$timerange[14], test$n[14]), 
rep(test$timerange[15], test$n[15]), rep(test$timerange[16], test$n[16]),

rep(test$timerange[17], test$n[17]), rep(test$timerange[18], test$n[18]), 
rep(test$timerange[19], test$n[19]), rep(test$timerange[20], test$n[20]),

rep(test$timerange[21], test$n[21]), rep(test$timerange[22], test$n[22]), 
rep(test$timerange[23], test$n[23]), rep(test$timerange[24], test$n[24]),

rep(test$timerange[25], test$n[25]), rep(test$timerange[26], test$n[26]), 
rep(test$timerange[27], test$n[27]), rep(test$timerange[28], test$n[28]),

rep(test$timerange[29], test$n[29]), rep(test$timerange[30], test$n[30]), 
rep(test$timerange[31], test$n[31]), rep(test$timerange[32], test$n[32]))


table <- table(CrimeCategory, TimeOfDay)
table

chisq.test(table)
```

#T Test

Given the significant p-value of our chi-square test statistic. We decided to conduct a hypothesis test to see how number of total crimes in San Francisco compares during the daylight and nightime.

We will now use the CLT to perform inference because the observations are 
independently selected and in this case, the sample size is large enough (n>30) 
for the CLT to apply. We are using t-distribution because we are testing a 
single sample's population mean and we don't know the true population SD.

$H_0:$ The true mean time of crimes committed during the week is equal to the true mean time of crimes committed during the weekend

$H_a:$ The true mean time of crimes committed during the week is less than true mean time of crimes committed during the weekend

$\alpha$ of 0.05

```{r crime_daylight_or_nighttime}
test_sanfrancrime <- important %>%
  mutate(weektype = case_when(DayOfWeek == "Saturday" ||
                              DayOfWeek == "Sunday" ~ "Weekend",
                              DayOfWeek == "Monday" ||
                              DayOfWeek == "Tuesday" ||
                              DayOfWeek == "Wednesday" ||
                              DayOfWeek == "Thursday" ||
                              DayOfWeek == "Friday" ~ "Weekday"))
test_sanfrancrime

# t.test(pacu30min_throatPain ~ treat,
#   data = tpafter30_2,
#   mu = 0,
#   var.equal = FALSE,
#   alternative = "greater",
#   conf.level = 0.95)
```




#Logistic Regression

#Mihir
By using logistic regression, we hope to answer the question of how much more
likely a violent crime is to occur depending on the time range of the crime
committed. This model below shows the predicted proportion of crimes that are
violent given the predictor of time range. The three time ranges used are
evening, morning, and night. We hypothesize that the highest proportion of 
violent crimes will occur at night because there are typically fewer witnesses
at these hours. 
```{r logistic model}
condensed <- important %>% 
  mutate(isViolent = ifelse(crimetype == "Violent", 1, 0)) %>% 
  select(DayOfWeek, PdDistrict, timerange, isViolent)
#condensed

mod1 <- glm(isViolent ~ DayOfWeek + timerange, data = condensed,
  family = "binomial")
tidy(mod1)


condensed2 <- important %>% 
  mutate(isProp = ifelse(crimetype == "Property", 1, 0)) %>% 
  select(DayOfWeek, PdDistrict, timerange, isProp)
#condensed2

mod2 <- glm(isProp ~ DayOfWeek + timerange, data = condensed2,
  family = "binomial")
tidy(mod2)
```



#4- How does time range affect whether crimes are violent? Kyra

```{r, echo = FALSE}
mod<- lm(yes_violent~timerange, 
         data = important3)
tidy(mod)
```


### RESULTS

#Chi-Square Test

The test statistic is 359.84, which has a chi squared distribution with 18
df under $H_0$. The p-value is < 2.2e-16 which is less than the $\alpha$ 
of 0.05. This means there is sufficient evidence to reject the null 
hypothesis. As a result, I conclude that there is sufficient evidence to 
suggest that at the 0.05 significance level that there is a relationship between
the crime types created above and categories for time of day created above.


#Logistic Regression

#Mihir
For Violent Crime: 

Predicted logit(p) = -2.280 + 0.077* (Mon.) + 0.127* (Tues.) + 0.035* (Wed.) +  
0.004* (Thur.) + 0.228* (Sat.) + 0.148* (Sun.) + 
0.137* (morning) + 0.227* (evening) + 0.608* (night)

For Property Crime: 

Predicted logit(p) = -0.417 + 0.035* (Mon.) - 0.013* (Tues.) - 0.046* (Wed.) -  
0.193* (Thur.) + 0.045* (Sat.) + 0.093* (Sun.) - 
0.114* (morning) + 0.396* (evening) - 0.109* (night)


#YUE: add quickly that we checked all conditions for regression, satisfied all conditions.



#Kyra
Predicted logit(yes_violent) = 
  0.10383 + 0.01188(evening) + 0.00227(morning) +0.06939(night)




### DISCUSSION

This section is a conclusion and discussion. This will require a summary of what you have learned about your research question along with statistical arguments supporting your conclusions. Also, critique your own methods and provide suggestions for improving your analysis. Issues pertaining to the reliability and validity of your data and appropriateness of the statistical analysis should also be discussed here. A paragraph on what you would do differently if you were able to start over with the project or what you would do next if you were going to continue work on the project should also be included.


#mihir's discussion:
After creating the the categoroical variables for time of day and also creating 
categorizing the types of crime within larger categories, we determined that
there was a statistically significant relationship between the time of day and
type of crime. As a result, I created a logistic model to calculate the log-odds 
of whether a violent crime occured with the predictors of day of the week and 
time of day. I also created a model for with the same predictors for a property 
crime.

This model cannot be applied to all cities but the base concept should remain 
the same. Most cities will have liekly have crime peak during the night and during
the weekends because more people will not be home.

I think if I were to continue to working the project I would likely break down
the model to apply it specific districts By doing so, the characteristics 
of these individual districts could be identified. Hopefully, these 
charactersitics allow us to potentially apply these models to districts with
similar population density, population breakdown, etc.



#Tina's disc:
After constructing the faceted visualization of crime count and time, we learned that certain categories of crime are far more prominent than others. For example, larceny/theft is more common, along with non-criminal crimes and assault. Most crimes happen during the afternoon and night, with the least happening in the hours from 0 to 6 (or in the early morning). Out of all the categories of crime listed, larceny/theft is mostly conducted during the evening, or between 6pm and 12am. This makes sense, as this is usually when night begins to set in, and it's a bit darker out, thus lending to increased obscurity and decreased acuity and vision-related impairments. Overall, this visualization displayed more crimes occurring during afternoons and evenings.

From a policy standpoint, government leaders in San Francisco should consider having additional police on duty during the times when crime is more eminent (afternoon and night). Another course of action could be to simply hire more police trained in Arceny, Theft, and Assault, as they were the most prominent from the faceted graph.

We understand that we cannot extrapolate our analysis to every city; however, our conclusions will be generalizable to similar cities to a moderate degree. Other cities with similar infrastructure and economic conditions are more likely to utilize the analysis we've found. This analysis will not be applicable to Durham, NC, for example, because of the population density and overall difference in cities (SF is a bustling city, while Durham is a smaller, quaint town).  

If we were to continue work on the project, we would add to our analysis by introducing data from different cities that are comparable to SF. It would be interesting to see the parallels in crime rates, as for many college students, traveling to their first job post-grad will be their first taste of independence and financial freedom -- thus, safety is an important factor to take into consideration. Ultimately, expanding the population of interest to citizens in multiple cities would give a better picture of how cases of crime occur differently by region, state, country, or population density (urban vs. rural). Second, we would also adjust for additional potential confounding variables to improve the accuracy of our analysis and models. Finally, to learn more, we'd want to speak with current or past residents and police officers about their experiences. Data is a great way to create thoughtful questions but it may not provide the full or complete answer.


#Kyra's discussion:

The bar graph that shows crime rates and violent crime proportions that is 
faceted by police districts shows valuable insight as to which police districts
are faced with the highest crime rates. The police districts of Tenderloin, 
Mission, and Ingleside have the highest percentages of violent crime (17.7%, 
16.6%, 16% respectively). However, it is Bayview, Northern, and Southern that 
have the highest total number of violent crimes (239, 202, 291 respectively). 
Park and Richmond were both consistent in having the lowest numbers of total 
violent crimes as well as proportion of violent crimes. Noting the success of 
these districts in maintaining low levels of crimes, it could be beneficial to 
restructure other districts to mirror their practices. 

Given that factors such as poverty level and unemployment
rates are main drivers for crime[1], it would be valuable to assess these numbers
for each police district. It would be valuable to know the differences in these
factors for districts with more and less crime so that next steps can be taken
to lower crime rates. For example, should a future study conclude that Park's
public education system has higher test scores than that of Bayview, improving
schools could be the best step for mitigating crime. 

An important factor that this analysis is lacking is the populations of each
police district. Having a larger population size would likely contribute to 
greater numbers of crime, even if per capita crime is lower. This information
is not present in the dataset we used, but would be necessary to extrapolate a
greater conclusion regarding which police district is most dangerous.


### REFERENCES

[1]https://poetsandquantsforundergrads.com/2020/05/15/are-these-the-50-best-metro-areas-for-recent-college-grads/

[2] https://www.sfchronicle.com/bayarea/article/Which-crimes-are-up-down-in-SF-during-15408485.php

[3] https://www.sfchronicle.com/bayarea/philmatier/article/SF-ranks-high-in-property-crime-while-it-ranks-14439369.php

[4] https://ucr.fbi.gov/hate-crime/2011/resources/variables-affecting-crime 


### NOTES

-notes from OH:
-connect to the next level
-interpret coefficients
-final repo should look like a paper from poli sci
-need to change order of days of the week
-need to add README file
- fix important2
- Mihir logistic regression - why only 3 time ranges 
- need to add coefficients 