---
title: "Staying Safe: Analyzing Crime in San Francisco"
subtitle: "2020 Vision"
author: "Mihir Patel, Tina Xia, Leah Okamura, Kyra Cooperman"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
sanfrancrimeBIG <- 
  read_csv("data/Police_Department_Incidents_-_Previous_Year__2016_.csv")

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
```

### INTRODUCTION AND DATA

San Francisco is a city known for its strong economy and booming tech industry. 
In addition to Silicon Valley and San Jose, the Bay Area is home to many
powerful companies such as Google, Tesla, Apple, and Cisco. Because of these 
many benefits, San Francisco is a popular destination for college graduates. In 
May 2020, San Francisco was ranked second as the best metro area for recent 
graduates. This especially took into consideration the "high wages, work from 
home ability, and a (mainly) pandemic-resilient economy" that many recent 
graduates worry about during this time [1]. 

However, with an overall crime rate in San Francisco that is 151% higher than 
the national average, it is also important to note that in recent years, San 
Francisco has not been the safest place to live. The SFChronicle reported that 
compared to 2019, "homicides increased by 21.4% in San Francisco from March to 
June of this year" [2]. There is a 1 in 15 chance of becoming a victim of any 
type of crime. A quick search about travel in San Francisco includes many 
articles listing the "Places to Avoid After Dark" or "Most Dangerous 
Neighborhoods in SF." With the a high possibility of any of us moving to San 
Francisco after our time at Duke, and the recent popularity with college 
graduates, we wanted to analyze this dataset to obtain conclusions about 
specific factors that correlate to higher levels of crime, which will could 
then inform us of some key insights we can keep during future travels or moves. 

Through our research, we plan to investigate what factors the general population
can associate with local crime in order to be the safest while in San Francisco.
Our main hypotheses are 1) a later time (e.g. nighttime hours) correlates to a 
higher level or rate of crime and 2) certain crimes are more prevalent during 
different times of the year. For example,if there is a strong correlation 
between night and rate of crime, then is there a correlation between which night
of the week (ex. Sunday night) and 
rate of crime? With location, are there certain districts that have a specific 
crime that is common there? By delving further and examining these 
relationships, we will be able to understand if crime has any specific pattern 
in San Francisco. We believe it is important to investigate this 
question because there likely are policy changes that can be implemented to 
increase safety throughout the city. Our investigation will shine light on
potential patterns of crime. 

In order to assess these hypotheses, we will look at the following relationships:
  1. Relationship between crime type and time
  2. Relationship between crime and time
  3. Relationship between violent crimes and police district
  4. Relationship between seasons and crime type

```{r dataglimpse}
set.seed(1)
sanfrancrime <- sanfrancrimeBIG %>%
  sample_n(15000)
```

The observations in the dataset are of crime data in San Francisco from 2016. We
found our dataset at https://www.kaggle.com/roshansharma/sanfranciso-crime-dataset. 
Each observation in this dataset is a crime whose various aspects have been 
recorded. There were originally 150,500 individual crimes/observations in this 
dataset. However, because of the nature of R Studio through OIT, we will be
taking a random and reproducible sample from the larger dataset. We created this
sample by using the function sample_n() on sanfrancrimeBIG to randomly select 
15,000 observations. We chose 15,000 because it is still large enough to get an 
accurate portrayal of the total data set, yet is much more manageable to process.

The curator of the dataset got it from the final assignment for Coursera and 
IBM's Data Visualization Course. The information in this dataset is most likely
directly from the San Francisco Police Department for their reported crimes 
during 2016. This dataset was originally used to practice analyzing and 
visualizing data through geo spatial mapping by using folium maps for 
geographical understanding. 


### METHODOLOGY

### Variables

We will analyze the validity of our hypotheses using various statistical 
methods, including a Chi-square test, logistic regression model, and hypothesis 
tests. The main variables we will be using in our analysis are Category, 
DayOfWeek, Date, Time, PdDistrict, and Resolution. We also created new variables
to assist us in our data. This includes the variable timerange, that organizes 
the hour of the day into four times of day "night", "morning", "day", and 
"evening", and a variable season, which organizes the observations by what 
season the crime was committed in. 

```{r creating time and filtering for important variables}
important <- sanfrancrime %>%
  mutate(str = as.character(Time)) %>%
  mutate(hourstr = substr(str, 1, 2)) %>%
  mutate (hour = as.numeric(hourstr)) %>% 
  mutate(month = as.numeric(substr(Date, 1, 2))) %>% 
  select(Category, DayOfWeek, Date, PdDistrict, Resolution, hour, month, X, Y)

important <- important %>% 
  mutate(timerange = case_when( hour >= 0 & hour < 6 ~ "dawn",
                                hour >= 6 & hour < 12 ~ "morning",
                                hour >= 12 & hour < 18 ~ "afternoon",
                                hour >= 18 & hour < 24 ~ "night"))

important <- important %>% 
  mutate(season = case_when(month >= 3 & month <= 5~ 'spring', 
                            month >= 6 & month <= 8 ~ 'summer',
                            month >= 9 & month <= 11 ~ 'autumn',
                            month == 12 | month == 1 | month == 2 ~ 'winter'))
```

We also decided to categorize the different types of crime that were reported. 
We organized the 39 types of crimes into variable crimetype, which consists of 
"Property", "Violent", "White Collar", "Drug/Alcohol", "Sex", "Suspicious", 
"Legal Violation", and "Miscellaneous". It is also important to note that we 
will be analyzing crime in the context of whether it was violent or not. 

```{r categorizing crime by type}
important <- important %>% 
  mutate(crimetype = case_when(
    
    Category == "BURGLARY" | Category == "LARCENY/THEFT" | 
    Category == "STOLEN PROPERTY" | Category == "RECOVERED VEHICLE" |
    Category == "VEHICLE THEFT" | Category == "ARSON" |
    Category == "VANDALISM"  ~ "Property",
    
    Category == "ROBBERY" | Category == "ASSAULT" | 
    Category == "KIDNAPPING" | 
      Category == "SEX OFFENSES, FORCIBLE" ~ "Violent",
    
    Category == "BRIBERY" | Category == "BAD CHECKS" | 
    Category == "EMBEZZLEMENT"| Category == "FORGERY/COUNTERFEITING" |
    Category == "FRAUD" | Category == "GAMBLING"| 
    Category == "EXTORTION" ~ "White Collar",
    
    Category == "DRIVING UNDER THE INFLUENCE" | Category == "DRUG/NARCOTIC" | 
    Category == "DRUNKENNESS"| Category == "LIQUOR LAWS" ~ "Drug/Alcohol",
    
    Category == "PORNOGRAPHY/OBSCENE MAT" | Category == "PROSTITUTION" |
    Category == "SEX OFFENSES, NON FORCIBLE" ~ "Sex",

    Category == "LOITERING" | Category == "TREA" | 
    Category == "TRESPASS"| Category == "SUSPICIOUS OCC" |
    Category == "DISORDERLY CONDUCT" ~ "Suspicious",
    
    Category == "WARRANTS"|Category == "WEAPON LAWS" |
    Category == "SECONDARY CODES" ~ "Legal Violation",

    Category == "MISSING PERSON" |Category == "NON-CRIMINAL"|
    Category == "OTHER OFFENSES" |Category == "SUICIDE"| 
    Category == "FAMILY OFFENSES" | Category == "RUNAWAY" ~ "Miscellaneous"))
```

### Visualizations

Because this data is from the San Francisco Police Department, Crime is not 
recorded by neighborhood but police district. To get a better understanding of 
how this may affect crime, we decided to visualize these districts as well as 
take a look at the number of crimes reported per district [5-7]. Because there 
is not a clear pattern between area and crime count, we will be using 
proportions when analyzing crime rates from district to district. 

```{r police districts}
library(sf)
sfran <- st_read("data/Current Police Districts-2", quiet = TRUE)


plot(sfran["district"], key.pos = 4, key.width = lcm(5), key.length = 1.0,
     main = "San Francisco Police Districts")
sanfrancrime%>%
  group_by(PdDistrict)%>%
  count()
```

```{r map-of-SF-with-crime-plotted}
ggplot(sfran) +
    geom_sf(color = "black", size = .5, fill = "#F5F2D0") +
     labs(title = "Current Police Districts in San Francisco With Crime in Color",
          subtitle = "High Concentration of Crime in Northeast SF", x = "Latitude", y = "Longitude", color = "Crime Type") +
  geom_point(data = important, aes(x = X, y = Y, color = crimetype), alpha = 0.5, size = .7)
```

This visualization shows the coordinate location of every crime committed. There
is a high concentration of crime in the Northeast region of San Francisco. 
Comparing this to our first map can tell us that Tenderloin, Central, Northern, 
and Mission are the districts where this concentration is. Property seems to be 
the most common crime followed by Miscellaneous and then Violent Crime. However,
this cannot be proven just from this visualization, so we need to visualize more
factors. 

```{r day of week and number of crimes}
library(forcats)
sanfrancrime$DayOfWeek <- factor(sanfrancrime$DayOfWeek, levels= c("Sunday", "Monday", 
    "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
day <- sanfrancrime%>%
  group_by(DayOfWeek)%>%
  mutate(cpday = n())%>%
  select(DayOfWeek, cpday)

ggplot(data = day, mapping = aes(x = DayOfWeek, fill = DayOfWeek)) +
    geom_bar()  + labs(x = "Day", y = "Count",
      title = "Number of Crimes Per Day Suggest Similar Spread of Crime") 
```

The next relationship we were interested in was if certain days had a higher 
rates of crime. We visualized this relationship by creating a bar graph that 
compares the day of the week and number of crimes each day. By looking at the 
visual, we are able to see that each has a relatively similar crime count 
compared to the other. Because this recorded over a whole year, it may be 
important to identify that Friday has the highest number of crimes while 
Sunday has the least, but overall there is no significant pattern that sticks 
out.


```{r day and crimetype}
important$DayOfWeek <- factor(important$DayOfWeek, levels= c("Sunday", "Monday", 
    "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
crimetypeday <-important%>%
  group_by(crimetype)%>%
  mutate(ctcount = n())

ggplot(data = important, mapping = aes(x = DayOfWeek)) +
  geom_bar(aes(fill = crimetype), position = "dodge") +
  labs(x = "Day of the Week", y = "Count", 
       title = "Overall Similar Distribution of Crime Type from Day to Day",
       fill= "Crime Type")
```

Because of the fairly equal distribution of crime by day, we decided to delve 
further by comparing each crime type by day. 
The faceted bar graph shows the frequency of each crime rate on a given day of 
the week. When looking at the visualization, it is easy to see a large 
difference between types of crime that exist. On each day, the number of 
property related crimes and miscellaneous crimes are significantly greater than 
the 5 other crime types. When looking at the frequency of crime types from day 
to day, every day has a relatively similar pattern of frequency. However, 
because of the variations in distribution throughout the week, we will be 
further investigating this relationship. 

```{r crimetype time of day}

important$timerange <- factor(important$timerange, levels= c("dawn", "morning", "afternoon", "night")) 
ggplot(data = important, mapping = aes(x = timerange)) +
  geom_bar(aes(fill = crimetype), position = "dodge") +
  labs(x = "Time of the Day", y = "Count", 
       title = "The Most Property Crime Occurs in the Latter Half of the Day",
       subtitle = "The Most Violent Also Crime Occurs in the Latter Half of the Day",
       fill= "Crime Type")
```

This then led us to the possibility that although day of the week may not have 
much of a relationship, this does not completely outrule time as a factor in how
a crime takes places. We visualized this by creating a bar graph comparing 
frequency of crime and time of day. The visualization proves that there is a 
clear difference in what part of the day that crime is committed. The greatest 
amount of property crime occurs during the night, followed by the afternoon. 
Overall, the latter half of the day is when a higher amount of crime is 
committed.

```{r PD vs Violent Crime}

 important3 <- important

 important3 <- important%>%
   filter(PdDistrict!="NA")%>%
   group_by(PdDistrict)%>%
   mutate(yes_violent = crimetype == "Violent")%>%
   arrange(desc(yes_violent))
 
 important3%>%
   group_by(PdDistrict)%>%
   count(yes_violent)%>%
   mutate(perc = (n/sum(n)*100))%>%
   arrange(desc(perc))%>%
   filter(yes_violent=="TRUE")%>%
   select(PdDistrict, n, perc)
 

ggplot(important3, aes(x = PdDistrict, fill = yes_violent))+
  geom_bar(position = "fill") + coord_flip()+
  labs(title =
         "Ingleside, Bayview, and Tenderloin Have Highest Violent Crime Rates ",
       y = "Proportion of Violent Crimes", x = "Police District", fill = "Violent Crime")
```

Followed by property and miscellaneous crime, violent crime was the most 
prevalent type of crime committed. Because violent crime typically indicates a 
worse degree of crime, we believed this would be an interesting relatonship to 
analyze. By looking at the table and bar plot, it is clear that Ingleside, 
Bayview, and Tenderloin have the highest rates of violent crime. However, 
Mission, Southern, and Bayview have the highest number of violent crimes. 
Park and Richmond both have the lowest rates and total numbers of violent 
crimes. For all police districts, the percentage of violent crimes is lower than
18%. 

```{r crime type and season}
important$season <- factor(important$season, levels= c("spring", "summer", "autumn", "winter"))
ggplot(data = important, mapping = aes(x = season)) +
  geom_bar(aes(fill = crimetype), position = "dodge") + 
  labs(title = "Distribution of Crime Suggests More 
       Property Crime in Autumn and Winter", fill = "Crime Type", x="Season",
       y = "Count")
```

We took a deep investigation of crime type vs day and time. This can provide 
insight to what individuals can possibly do to be safer. However, we also wanted
to visualize this on a broader perspective and see if certain seasons had a 
greater amount of a certain type of crime or overall crime. After analyzing this
bar plot, we can conclude that the distribution of crime type is similar across 
all seasons. However, because this visualization is the number of crimes 
throughout the whole year, we are interested if the higher number of property 
crime in autumn and winter is significant. 

# Chi-Square Test

The visualization between crime type and time of day left us unsure if a 
relationship existed between these two variables. So, we will be performing a 
Chi-Squared test between the crime types and categorical time of day to 
determine if there is the relationship between them is statistically significant.

$H_0:$ There is NO relationship between the crime type and categories for
time of day.

$H_a:$ There IS a relationship between the crime type and 
categories for time of day.
 
$\alpha$ of 0.05

```{r chi-squared test for crime type and timerange}

crimecount <- important %>%
  count(crimetype)

test <- important %>%
  group_by(crimetype) %>%
  count(timerange)

CrimeCategory <- c(rep(crimecount$crimetype[1], crimecount$n[1]),
               rep(crimecount$crimetype[2], crimecount$n[2]),
               rep(crimecount$crimetype[3], crimecount$n[3]),
               rep(crimecount$crimetype[4], crimecount$n[4]),
               rep(crimecount$crimetype[5], crimecount$n[5]),
               rep(crimecount$crimetype[6], crimecount$n[6]),
               rep(crimecount$crimetype[7], crimecount$n[7]),
               rep(crimecount$crimetype[8], crimecount$n[8]))

TimeOfDay <- c(
rep(test$timerange[1], test$n[1]), rep(test$timerange[2], test$n[2]), 
rep(test$timerange[3], test$n[3]), rep(test$timerange[4], test$n[4]),

rep(test$timerange[5], test$n[5]), rep(test$timerange[6], test$n[6]), 
rep(test$timerange[7], test$n[7]), rep(test$timerange[8], test$n[8]),

rep(test$timerange[9], test$n[9]), rep(test$timerange[10], test$n[10]), 
rep(test$timerange[11], test$n[11]), rep(test$timerange[12], test$n[12]),

rep(test$timerange[13], test$n[13]), rep(test$timerange[14], test$n[14]), 
rep(test$timerange[15], test$n[15]), rep(test$timerange[16], test$n[16]),

rep(test$timerange[17], test$n[17]), rep(test$timerange[18], test$n[18]), 
rep(test$timerange[19], test$n[19]), rep(test$timerange[20], test$n[20]),

rep(test$timerange[21], test$n[21]), rep(test$timerange[22], test$n[22]), 
rep(test$timerange[23], test$n[23]), rep(test$timerange[24], test$n[24]),

rep(test$timerange[25], test$n[25]), rep(test$timerange[26], test$n[26]), 
rep(test$timerange[27], test$n[27]), rep(test$timerange[28], test$n[28]),

rep(test$timerange[29], test$n[29]), rep(test$timerange[30], test$n[30]), 
rep(test$timerange[31], test$n[31]), rep(test$timerange[32], test$n[32]))


table <- table(CrimeCategory, TimeOfDay)
table

chisq.test(table)
```


# Logistic Regression

Violent crime typically presents the greatest amount of danger, so by using 
logistic regression, we hope to answer the question of how much more
likely a violent crime is to occur depending on the time range of the crime
committed. These models below show the predicted proportion of violent crimes 
and property crimes given the predictor of time range. The four time ranges 
used are dawn, morning, afternoon, and night. Before using regression, we 
checked that the necessary conditions were met. 

```{r logistic model}
condensed <- important %>% 
  mutate(isViolent = ifelse(crimetype == "Violent", 1, 0)) %>% 
  select(DayOfWeek, PdDistrict, timerange, isViolent)

mod1 <- glm(isViolent ~ DayOfWeek + timerange, data = condensed,
  family = "binomial")
tidy(mod1)


condensed2 <- important %>% 
  mutate(isProp = ifelse(crimetype == "Property", 1, 0)) %>% 
  select(DayOfWeek, PdDistrict, timerange, isProp)

mod2 <- glm(isProp ~ DayOfWeek + timerange, data = condensed2,
  family = "binomial")
tidy(mod2)
```

# Hypothesis Tests

We will now use the CLT to perform inference because the observations are 
independently selected and in this case, the sample size is large enough (n>30) 
for the CLT to apply. We are using t-distribution because we are testing a 
single sample's population mean and we don't know the true population SD.


### t test for Violent Crime

The logistic regression predicted that the combination of Saturday and Dawn 
would have the greatest likelihood of a violent crime occurring. As a result, 
we are exploring the significance of this relationship with a t-test.

$H_0$: Saturdays at Dawn have the SAME likelihood of a violent crime occurring 
as the sample population.

$H_a$: Saturdays at Dawn have a GREATER likelihood of a violent crime occurring 
than the sample population.

$\alpha$ of 0.05    

```{r violent crime predicted target t-test}
pls <- important %>% 
  mutate(targeted = ifelse(DayOfWeek == "Saturday" & timerange == "dawn", 1, 0)) %>% 
  mutate(is_Violent = ifelse(crimetype == "Violent", 1, 0))

t.test(data = pls,
       is_Violent ~ targeted,
       conf.level = 0.95,
       alternative = "less",
       ver.equal = FALSE)
```

### t test for Property Crime

The logistic regression predicted that the combination of Sunday and Night would
have the greatest likelihood of a property crime occurring. As a result, we are 
exploring the significance of this relationship with a t-test.

$H_0$: Sunday at Night have the SAME likelihood of a property crime occurring as
the sample population.

$H_a$: Saturdays at Night have a GREATER likelihood of a property crime 
occurring than the sample population.

$\alpha$ of 0.05    

```{r t test pt2}
yeet <- important %>% 
  mutate(targeted = ifelse(DayOfWeek =="Sunday" & timerange == "night", 1, 0)) %>% 
  mutate(is_Property = ifelse(crimetype == "Property", 1, 0))

t.test(data = yeet,
       is_Property ~ targeted,
       conf.level = 0.95,
       alternative = "less",
       ver.equal = FALSE)
```

### t test for Property Crime in Autumn and Winter

$H_0:$ Property crime is EQUALLY likely to occur during colder seasons Autumn 
and Winter than compared to other
seasons

$H_a:$ Property crime is MORE likely to occur during the colder seasons 
(Autumn and Winter)

$\alpha$ of 0.05

```{r t testing weather}
summercheck <- important %>%
  mutate(is_cold = ifelse(season == "autumn" | season == "winter", 1, 0)) %>%
  mutate(is_Property = ifelse(crimetype == "Property", 1, 0))

t.test(data = summercheck,
       is_Property ~ is_cold,
       conf.level = 0.95,
       alternative = "less",
       ver.equal = FALSE)
```

### RESULTS

# Chi-Square Test

The test statistic is 359.84, which has a chi squared distribution with 18
df under $H_0$. The p-value is < 2.2e-16 which is less than the $\alpha$ 
of 0.05. This means there is sufficient evidence to reject the null 
hypothesis. As a result, I conclude that there is sufficient evidence to 
suggest that at the 0.05 significance level that there is a relationship between
the crime types created above and categories for time of day created above.


# Logistic Regression

For Violent Crime: 

Predicted logit(p) = -1.524 - 0.071* (Mon.) - 0.021* (Tues.) - 0.114* (Wed.) - 
0.145* (Thur.) - 0.148* (Fri.) + 0.079 * (Sat.) - 0.471* (morning) -
0.608* (afternoon) - 0.381* (night)

The reference level is Sunday at Dawn. While holding the day of the week 
constant, the log odds of a violent crime occurring decreases by 0.471 if 
morning, 0.608 if afternoon, and 0.381 if it is night. While holding the time 
range of the day constant, and on average, the log odds of a violent crime 
occurring decreases by 0.071 if Monday, 0.021 if Tuesday, 0.114 if Wednesday, 
0.145 if Thursday, and 0.148 if it is Friday. However, the log-odds increase by 
0.079 if it is Saturday. According to the model, the log-odds of a violent crime
occurring is greatest when it is Saturday at Dawn and the least when it is 
Friday at Afternoon.

For Property Crime: 

Predicted logit(p) = -0.324 - 0.058* (Mon.) - 0.107* (Tues.) - 0.140* (Wed.) -  
0.287* (Thur.) - 0.093* (Fri.) - 0.048* (Sat.) - 0.006* (morning) +
0.109* (afternoon) + 0.505* (night)

The reference level is Sunday at Dawn. While holding the day of the week 
constant, the log odds of a violent crime occurring decreases by 0.006 it is 
morning. However, the log-odds increase by 0.109 if afternoon and 0.505 if it is
night. While holding the time range of the day constant, and on average, the log
odds of a violent crime occurring  decreases by -0.058 if Monday, -0.107 if 
Tuesday, -0.140 if Wednesday, -0.287 if Thursday, -0.093 if Friday, and -0.048 
if it is Saturday. According to the model, the log-odds of a violent crime 
occurring is greatest when it is Sunday at Night and the least when it is 
Thursday at Morning.


### Hypothesis Tests

### t test for Violent Crime
After creating our visualizations, we noticed that Saturday at dawn seemed to be
a point of significance; thus, we wanted to see if the predicted target 
(Saturday at dawn) truly had a greater likelihood of violent crime occurring 
than the sample population.

t = -5.0675, degrees of freedom = 381.07.

Our p-value < 3.149e-07, so we reject the null hypothesis at the $\alpha$  = 
0.05 significance level. Thus there is sufficient evidence to suggest that 
predicted target (Saturday at dawn) has a GREATER likelihood of violent crime 
occurring than the sample population, which confirmed our suspicions. 

### t test for Property Crime
After creating our visualizations, we noticed that Sunday nights seemed to be a 
time of significance. We wanted to further explore and see if this predicted 
target truly had a greater likelihood of violent crime occurring than the sample
population.

t = -2.6675, degrees of freedom = 622.8. Our p-value is 0.00392, so we reject 
the null hypothesis at the $\alpha$  = 0.05 significance level. Thus there is 
sufficient evidence to suggest that our predicted target of Sunday nights truly 
had a greater likelihood of violent crime occurring than the sample population, 
which confirmed our suspicions. Intuitively, this makes sense, as nighttime 
hours lends itself to additional obscurity.

### t test for Property Crime in Autumn and Winter
In our visualization relating to seasonal differences and SF crime, we noticed 
that winter seasons seemed to have more crime. Thus, we wanted to further 
explore and see if property crime is more likely to occur in the colder seasons 
(Autumn and Winter).

t = -2.4695, degrees of freedom = 14996. Our p-value is 0.006771, so we reject 
the null hypothesis at the $\alpha$  = 0.05 significance level. Thus there is 
sufficient evidence to suggest that property crime is more likely to occur in 
the colder seasons (Autumn and Winter), which confirms one of our main 
hypotheses.


### DISCUSSION

When trying to be safest in the busy city of San Francisco, we discovered 
through our analysis that certain measures can be taken to improve one's safety.
This is proven by the multiple factors that influence where, what, and when 
crime is committed. However, it might first be important to discuss which 
factors do not play a substantial role in the act of a crime. For example, when 
looking at the bar graph comparing day of the week and number of crimes, it is 
clear that the difference from day to day is very minimal. Therefore, looking at
just the day itself should not be a factor to whether it may be more dangerous 
or not. However, looking at the visualization comparing type of crime and day of
week shows that each day has a spread where Property Crime is the highest, 
followed by Miscellaneous Crime, followed by Violent Crime. Something that could
cause a possible influence in our data is the fact that the variable crime type 
was created by us, so the organization of what crime fits into what category and
the creation of categories is based on our research and knowledge. 

In addition, after creating categorical variables for time of day and also 
categorizing the types of crime within larger categories, we determined that 
there was a statistically significant relationship between the time of day and 
type of crime. As a result, we created a logistic model to calculate the 
log-odds of whether a violent crime occurred with the predictors of day of the 
week and time of day. We also created a model with the same predictors for 
property crime. These two models predicted that violent crime was most likely to
occur on Saturday at dawn and property crime Sunday nights. We then proved these
predictors by conducting hypothesis test and concluded a statistically 
significant p-value. Based on this, residents can be advised to avoid leaving 
their homes during the early hours of Saturday as well as investing in home 
security or surveillance to prevent or catch possible crime to their property. 
In addition, this conclusion can help inform police districts of how to better 
use their resources to be more efficient. However, this model cannot be applied 
to all cities; the base concept should remain the same. Cities with similar 
infrastructure, economic level, etc. will likely have crime peak during the 
night and during the weekends like that of San Francisco. The last hypothesis 
test proved that Autumn and Winter had a significant increase in crime versus 
the other two seasons. This information can be used to find different trends 
during this time and possibly implement different practices such as seasonal 
hiring of officers. 

The bar graph that shows crime rates and violent crime proportions that is 
faceted by police districts shows valuable insight as to which police districts
are faced with the highest crime rates. The police districts of Tenderloin, 
Bayview, and Ingleside have the highest percentages of violent crime, while 
Park and Richmond were both consistent in having the lowest proportion of 
violent crimes. Noting the success of these districts in maintaining low 
levels of crimes, it could be beneficial to restructure other districts to
mirror their practices.

An important factor that this analysis is lacking is the populations of each 
police district. Having a larger population size would likely contribute to 
greater numbers of crime, even if per capita crime is lower. This information 
is not present in the dataset we used, but would be necessary to extrapolate a
greater conclusion regarding which police district is most dangerous. Given 
that factors such as poverty level and unemployment rates are main drivers for 
crime [1], it would be valuable to assess these numbers for each police 
district. It would also be important to know the differences in these factors 
for districts with more and less crime so that next steps can be taken to lower
crime rates. For example, should a future study conclude that Park’s public 
education system has higher test scores than that of Bayview, improving schools
could be the best step for mitigating crime.

From a policy standpoint, government leaders in San Francisco could consider 
having additional police on duty during the times when crime is more eminent 
(afternoon and night). However, this is only one possible solution. More 
research could find that times where crime is more eminent is not a result 
of less police on duty, but a varity of other factors that are not included in
this dataset. Because of this, there is number of solutions that could help 
lessen crime during these times. While an increase in police surveillance could 
also result in a decreasse of property crime, this is not necessarily the same 
for violent crime as more police on duty could cause more crimes to be reported. 

Again, we understand that we cannot extrapolate our analysis to every city;
however, our conclusions are generalizable to similar cities to a moderate 
degree. Other cities with similar infrastructure and economic conditions are 
more likely to utilize the analysis we've found — this analysis will not be
applicable to Durham, NC, for example, because of the population density and 
overall difference in cities (SF is a bustling city, while Durham is a smaller,
quaint town).  

If we were to continue work on the project, we would add to our analysis by 
introducing data from different cities that are comparable to San Francisco. 
It would be interesting to see the parallels in crime rates, as for many college
students, traveling to their first job post-grad will be their first taste of 
independence and financial freedom -- thus, safety is an important factor to 
take into consideration. Ultimately, expanding the population of interest to 
citizens in multiple cities would give a better picture of how cases of crime 
occur differently by region, state, country, or population density (urban vs. 
rural). Second, we would also adjust for additional potential confounding 
variables to improve the accuracy of our analysis and models. Finally, to learn 
more, we'd want to speak with current or past residents and police officers 
about their first-hand local experiences with crime. Data is a great way to 
create thoughtful questions but it may not provide the full or complete answer.



### REFERENCES

[1] Allen, Nathan. “Are These The 50 Best Metro Areas For Recent College Grads?”
Poets&Quants for Undergrads, 15 May 2020, poetsandquantsforundergrads.com/2020
/05/15/are-these-the-50-best-metro-areas-for-recent-college-grads/.

[2] Hwang, Kellie. “Amid the Pandemic, Overall Crime in SF Is down. But These 
Crimes Are Up.” SFChronicle.com, San Francisco Chronicle, 15 July 2020, www.sfchronicle.com/bayarea/article/Which-crimes-are-up-down-in-SF-during-
15408485.php.
  
[3] Matier, Phil. “SF Ranks High in Property Crime While It Ranks Low in Arrests
.” SFChronicle.com, San Francisco Chronicle, 15 Sept. 2019, www.sfchronicle.com/bayarea/philmatier/article/SF-ranks-high-in-property-crime-
while-it-ranks-14439369.php.

[4] “Variables Affecting Crime.” FBI, FBI, 5 Nov. 2012, ucr.fbi.gov/hate-crime/
2011/resources/variables-affecting-crime.

[5] “5. Plotting Simple Features.” Sf, r-spatial.github.io/sf/articles/sf5.ht
  ml#geometry-with-attributes-sf-1.
  
[6] Benjamin Chang Sorensen. “Policing Trends in San Francisco.” Benjamin 
  Chang Sorensen, 29 June 2018, www.benjaminsorensen.me/project/sf_police/. 
  
[7] “Current Police Districts: DataSF: City and County of San Francisco.” San 
  Francisco Data, data.sfgov.org/Public-Safety/Current-Police-Districts/wk
  hw-cjsf.
